---
title: "Exercise 2"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
  word_document: default
---
EMAIL: n.c.deschipper

Question 1
part 1
1.1
population standard error of the mean difference, you can estimate this with SE of student t and SE of welch

1.2
$\sqrt{\frac{208}{208}}$



```{r}

```

1.3
Input:
S: integer deining the number of independent data sets to generate
n: the sample size of the data sets
 $\mu$, and $\sigma^2$ vlaues fo the population parameters ofthe data generating        distribution
 Output: S estimates o the statistics of interest, namely bias, variance, MSE and RE
 
1. initialize out students_bias, students_var, students_mse, welch_bias, welch_var,      welch_mse and relative_efficiency all as vector of length S
2. For s in 1:S:
  A. Generate data with sample size n1 from N($\mu\_{1}$ , $\sigma^{2}\_{1}$) and sample size n2 from N($\mu\_{2}$ , $\sigma^{2}\_{2}$)
  B. Obtain sample variance, bias and mse for both
  
  
1. $intialize bias\_{student}, variance\_{student}, mse\_{student} , bias\_{welch}, variance\_{welch} , mse\_{welch}  all as vector of lentgh S and RE for relative efficency$
  
  
  


  
  
  
  
  
  
  
```{r}
set.seed(200)
n1 <- c(10, 100, 200)
n2 <- 200
var2 <- c(1, 2 , 10)
var1 <- 1
mean1 <- 0
mean2 <- 1
S <- 10000
conditions <- expand.grid(n1, var2)

MonteCarlo_SE <- function(n1, var2) {
  data_1 <- rnorm(n1, mean1, sqrt(var1))
  data_2 <- rnorm(n2, mean2, sqrt(var2))
  SE_student <- rep(NA, S)
  SE_welch <- rep(NA, S)
  for (i in 1:S) {
    data_1 <- rnorm(n1, mean1, sqrt(var1))
    data_2 <- rnorm(n2, mean2, sqrt(var2))
    pooled_sd <- sqrt(((n1-1)*var(data_1)+(n2-1)*var(data_2))/(n1+n2-2))
    SE_student[i] <- pooled_sd*sqrt(((1/n1)+(1/n2)))
    SE_welch[i] <- sqrt((var(data_1)/n1)+(var(data_2)/n2))
  }
  bias_Student <- sqrt((var1/n1)+(var2/n2)) - mean(SE_student)
  bias_Welch <- sqrt((var1/n1)+(var2/n2)) - mean(SE_welch)
  Out_variance_student <- var(SE_student)
  Out_variance_welch <- var(SE_welch)
  Out_bias_student <- bias_Student
  Out_bias_welch <- bias_Welch
  Out_MSE_student <- (bias_Student)^2 + Out_variance_student
  Out_MSE_welch <- (bias_Welch)^2 + Out_variance_welch
  RE <- ((Out_MSE_student)/(Out_MSE_welch))
  return(c(Out_variance_student, Out_variance_welch, Out_bias_student, Out_bias_welch, Out_MSE_student, Out_MSE_welch, RE))
}

results <- matrix(NA, 7, 9)
for (i in 1:nrow(conditions)) {
  results[, i] <- MonteCarlo_SE(n1 = conditions[i, 1], var2 = conditions[i,2])
}

out_results <- cbind(conditions, t(round(results, digits = 3)))
colnames(out_results) <- c("n1", "var2", "Variance_S", "variance_W", "Bias_S", "Bias_W", "MSE_S", "MSE_W", "Relative Efficiency")
out_results


```
1.2
Use t-test r-function to obtain p value
Null hypothesis: The means of the two t-tests are the same
Alternative Hypothesis: The means of the two t-tests are not the same

2.1
Null hypothesis: The means of the two t-tests are the same
Alternative Hypothesis: The means of the two t-tests are not the same

2.2





```{r}
n1 <- c(10, 100, 200)
n2 <- 200
var1 <- 2
var2 <- c(1, 2, 10)
mean1 <- 0
mean2 <- 1
conditions <- expand.grid(n1, var2)

```




